Final paper detail checks and analyses

### 2021-03-03 Final_analyses_checks_notebook.Rmd
added retrospective prepandemic ttests and glad edgi sensitivity
updated sample composition for final checks

retrospective
```{r means etc by sample retro}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.retro = mean(gad.sum_score_retro, na.rm = TRUE),
            sd.gad.retro = sd(gad.sum_score_retro, na.rm = TRUE),
            n.gad.retro = sum(!is.na(gad.sum_score_retro)),

@@

prepandemic
```{r means etc by sample prepan}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.prepan = mean(gad.sum_score_prepan, na.rm = TRUE),
            sd.gad.prepan = sd(gad.sum_score_prepan, na.rm = TRUE),
            n.gad.prepan = sum(!is.na(gad.sum_score_prepan)),

@@

@@

dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)

@@

Retrospective PHQ
```{r ttest average by sample retro phq}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$parameter)

@@

Prepandemic GAD
```{r ttest average by sample prepan gad}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$parameter)

@@

Prepandemic PHQ
```{r ttest average by sample prepan phq}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$parameter)
```

@@

dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(pcl.sum_score_base,pcl.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$p.value,
         t_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$statistic,
         df = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$parameter)

>>>>

retrospective
```{r means etc by sample retro}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.retro = mean(gad.sum_score_retro, na.rm = TRUE),
            sd.gad.retro = sd(gad.sum_score_retro, na.rm = TRUE),
            n.gad.retro = sum(!is.na(gad.sum_score_retro)),

@@

prepandemic
```{r means etc by sample prepan}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.prepan = mean(gad.sum_score_prepan, na.rm = TRUE),
            sd.gad.prepan = sd(gad.sum_score_prepan, na.rm = TRUE),
            n.gad.prepan = sum(!is.na(gad.sum_score_prepan)),

@@

Prepandemic compared to retrospective
(no retrospective ratings for PCL)
```{r ttest for average scores retro compred to prepan}
t.test(dat.prepan$gad.sum_score_prepan,dat.prepan$gad.sum_score_retro, paired = T)
t.test(dat.prepan$phq.sum_score_prepan,dat.prepan$phq.sum_score_retro, paired = T)
```

@@

dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD"  ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)

@@

Retrospective PHQ
```{r ttest average by sample retro phq}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR"| Sample == "EDGI" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$parameter)

@@

Prepandemic GAD
```{r ttest average by sample prepan gad}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$parameter)

@@

Prepandemic PHQ
```{r ttest average by sample prepan phq}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD"  ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$parameter)
```

@@

dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR"| Sample == "EDGI"  ~ "NBR")) %>%
  select(pcl.sum_score_base,pcl.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$p.value,
         t_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$statistic,
         df = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$parameter)
